INSTRUCTIONS FOR AUTHORS OF POSTER ABSTRACTS USING \LaTeX

### 2015-04-17 paper/paper_version2.tex
04/17/15

@@

\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$.     
\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
\WHILE{$x\in\mbox{max}_{x\in A} q_{tx}\left(A\right)<P$}
\WHILE{$\mbox{min}_{x\in A} q_{tx}\left(A\right) \le c$}
 \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
\STATE Remove $x$ from $A$.
\ENDWHILE    
\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.     \STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.    
\STATE Increment $t$.
 \ENDWHILE
  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Z_{tx} / n_{tx}$ as our estimate of the best.

@@

The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
onto selection decisions. Specifically, this mapping finds the first
time.

The same distribution over selection decision will result if we apply
the same same selection process to the following time process with
jumps at $t\in\left\{ 0,\delta^{2},2\delta^{2},\ldots\right\} =\delta^{2}\mathbb{N}$,
\[
q'_{tx}\left(A\right)=q'\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
\]
Later, we can approximate the previous process by the continuous time
process
\begin{eqnarray}
q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001}
\end{eqnarray}
where $t\geq0$ . Then we will show the difference in selection decisions
vanishes as $\delta\rightarrow0$.

After that, we would like to use a kind of central limit theorem for
$Z_{\frac{t}{\delta^{2}}x}=Y_{n_{x}\left(t/\delta^{2}\right),x}$
when $\delta$ goes to zero to work with a Brownian motion instead.
Specifically, we are going to see that the the standardized sum of
the output data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
that are right-continuous and have left-hand limits, with the Skorohod
topology. The definition and the properties of this topology may be
found in Chapter 3 of Billingsley 1999 and the appendix. We will first
see this result because it will give us a clue for proving the asymptotic
validity of the Algorithm 2.

@@

We now gain the insight that we were looking for. We will use $\mathcal{C}_{x}\left(\delta,\cdot\right)$
instead of $Z_{\frac{t}{\delta^{2}}x}$ in $\left(1\right)$, which
is the definition of $q_{tx}\left(A\right)$,
\[
q_{tx}\left(A\right)=q'\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right),
\]
the previous equation is true because 
\[
Z_{\frac{t}{\delta^{2}}x}=C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right).
\]

@@

In order to prove this, we first prove Lemma 2, which will allow us
to use Theorem 5.5 of Billingsley 1968, which implies the desired
result.

>>>>

For each $t$, $x\in\left\{ 1,\ldots,k\right\} $, and subset $A\subset\left\{ 1,\ldots,k\right\} $,
we define a function
\[
q'_{tx}\left(A\right)=\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx}}{n_{tx}}\right)\left/\sum_{x'\in A}\mbox{exp}\left(\delta\beta_{t}\frac{Z_{tx'}}{n_{tx'}}\right),\right.\mbox{ }\beta_{t}=\frac{\sum_{x'\in A}n_{tx'}}{\sum_{x'\in A}\hat{\lambda}_{tx'}^{2}}
\]
where $\hat{\lambda}_{tx'}^{2}$ is the sample variance of all samples
from alternative $x$ thus far and $Z_{tx}=Y_{n_{tx},x}$.

@@

\STATE For each $x$, sample alternative $x$ $n_0$ times and set $n_{0x} \leftarrow n_0$.     
Let $W_{0x}$ and $\lambdahat^2_{0x}$ be the sample mean and sample variance respectively of these samples.     Let $t\leftarrow 0$.Let $z \in \mbox{arg max}_{x\in A} \lambdahat^2_{tx}$.     
\STATE Let $A \leftarrow \{ 1,\ldots, k\}$, $\upthresh \leftarrow P^*$.
\WHILE{$x\in\mbox{max}_{x\in A} q'_{tx}\left(A\right)<P$}
\WHILE{$\mbox{min}_{x\in A} q'_{tx}\left(A\right) \le c$}
 \STATE Let $x\in\mbox{arg min}_{x\in A} q_{tx}\left(A\right)$.
    \STATE Let $\upthresh \leftarrow \upthresh/(1-q_{tx}\left(A\right))$.     
\STATE Remove $x$ from $A$.
\ENDWHILE    
\STATE For each $x\in A$, let      $n_{t+1,x} = \ceil\left( \lambdahat^2_{tx} (n_{tz} + B_z) / \lambdahat^2_{tz} \right)$.     \STATE For each $x\in A$, if $n_{t+1,x}>n_{tx}$, take $n_{t+1,x}-n_{tx}$ additional samples from alternative $x$.  Let $W_{t+1,x}$ and $\lambdahat^2_{t+1,x}$ be the sample mean and sample variance respectively of all samples from alternative $x$ thus far.    
\STATE Increment $t$.
 \ENDWHILE
  \STATE Select $\xhat \in\mbox{arg max}_{x\in A} Z_{tx} / n_{tx}$ as our estimate of the best.

@@

The third maps the paths of $\left(q_{tx}^{'}\left(A\right):t\in\mathbb{N},A\subset\left\{ 1,\ldots,k\right\} ,x\in A\right)$
onto selection decisions. Specifically, this mapping finds the first
time that $\mbox{max}_{x\in A}q_{tx}\left(A\right)$ is larger than
some threshold $P$, and then it chooses the system with the largest
empirical mean $Z_{tx}/n_{tx}$.

Later, we can approximate the previous process by the continuous time
process
\begin{eqnarray}
q_{tx}\left(A\right) & = & q\left(\left(Z_{\frac{t}{\delta^{2}}x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right)\label{eq:0.001-1}
\end{eqnarray}
where $t\geq0$ . Then we will show the difference in selection decisions
vanishes as $\delta\rightarrow0$.

After that, we would like to use a kind of central limit theorem for
$Z_{\frac{t}{\delta^{2}}x}$ when $\delta$ goes to zero to work with
a Brownian motion instead. In order to do this, we are going to rewrite
equation (1) in terms of a centralized version of $Z$:

\[
\mathcal{C}_{x}\left(\delta,t\right)=\frac{Y_{n_{x}\left(t\right),x}-t\lambda_{x}^{2}\mu_{x}}{\frac{\lambda_{x}^{2}}{\lambda_{z}\delta}}
\]
and the resulting expresion is

\[
q_{tx}\left(A\right)=q\left(\left(C_{x}\left(\delta,t\right)\frac{\lambda_{x}^{2}}{\delta\lambda_{z}^{2}}+\frac{\lambda_{x}^{2}}{\lambda_{z}^{2}}\left(n_{0}+\frac{t}{\delta^{2}}\right)\delta a_{x},\frac{t}{\delta^{2}}:x\in A\right),\delta,A\subset\left\{ 1,\ldots,k\right\} \right).
\]

Thus, we can see the selection decision resulting from the BIZ algorithm
as the result of applying some mapping $f\left(\cdot,\delta\right)$
to the paths $t\mapsto\mathcal{C}_{x}\left(\delta,t\right)$ .

The last part of our proof is to observe that (1) $\mathcal{C}\left(\delta,\cdot\right)$
converges to a multivariate Brownian motion $W$ as $\delta$ goes
to 0; (2) the function $f$ has a continuity property that causes
\[
f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)\Rightarrow g\left(W\right)
\]
where g is the selection decision from applying the BIZ procedure
in continuous time; and (3) the BIZ procedure satsifies the IZ guarantee
when applied in continuous time.

First, we are going to see that the the standardized sum of the output
data converges to a Brownian motion in the sense of $D_{\infty}:=D[0,\infty)$,
which is the set of functions from $\left[0,\infty\right)$ to $\mathbb{R}$
that are right-continuous and have left-hand limits, with the Skorohod
topology. The definition and the properties of this topology may be
found in Chapter 3 of Billingsley 1999 and the appendix.

@@

@@

In order to prove this, we first prove a continuity property in Lemma
2, which will allow us to use Theorem 5.5 of Billingsley 1968, which
implies the desired result.

### 2015-04-17 paper/wsc15LatexPaper/wsc15poster.tex
04/17/15

%**************************************************************************
%*
%*  Paper: ``INSTRUCTIONS FOR AUTHORS OF LATEX DOCUMENTS''
%*
%*  Publication: 2015 Winter Simulation Conference Author Kit
%*
%*  Filename: wsc15paper.tex
%*
%*  Date: January 31, 2001   Time:  9:45 PM
%*      BASE of current version: Feb 01, 2010 (primary WSC'10 LaTeX file)
%*
%*  Word Processing System: TeXnicCenter and MiKTeX
%*
%*
%*  All files need the following
\input{wsc15style.tex}     % download from author kit.  Style files for wsc formatting. Don't remove this line - required for generating the final paper!

\documentclass{wscpaperproc}
\usepackage{latexsym}
%\usepackage{caption}
\usepackage{graphicx}
\usepackage{mathptmx}

%
%****************************************************************************
% AUTHOR: You may want to use some of these packages. (Optional)
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
% Private macros here (check that there is no clash with the style)
\newcommand{\lambdahat}{\widehat{\lambda}}
\newcommand{\xtilde}{\tilde{x}}
\newcommand{\qhat}{\widehat{q}}
\newcommand{\as}{\ a.s.}
\newcommand{\zap}[1]{}
\newcommand{\Ncal}{\mathcal{N}}
\newcommand{\sigmahat}{\hat{\sigma}}
\newcommand{\Nat}{\mathbb{N}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Pb}[2]{\mathbb{P}_{#1}\left\{#2\right\}}
\newcommand{\Ybar}{\overline{Y}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
% \newcommand{\argmax}{\operatornamewithlimits{arg\,max}}
% \newcommand{\argmin}{\operatornamewithlimits{arg\,min}}
\newcommand{\g}{\,\vert\,}
\newcommand{\ind}[1]{1_{\left\{#1\right\}}}
\newcommand{\Fcal}{\mathcal{F}}
\newcommand{\Gcal}{\mathcal{G}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\xhat}{\hat{x}}
\newcommand{\xwig}{\tilde{x}}
\newcommand{\PZ}{\mbox{PZ}}
\newcommand{\PCS}{\mbox{PCS}}
\newcommand{\PGS}{\mbox{PGS}}
\newcommand{\uLFC}{\underline{u}}
\newcommand{\e}[1]{\left\{ #1 \right\}}
\newcommand{\T}{\mathbb{T}} % Time index set.
\newcommand{\CS}{\mbox{CS}}
\newcommand{\Ft}{\mathcal{F}_t}
\newcommand{\F}[1]{\mathcal{F}_{#1}}
\newcommand{\Ftau}{\mathcal{F}_\tau}
\newcommand{\Rcal}{\mathcal{R}}
\newcommand{\upthresh}{P}
\newcommand{\xstar}{X^*}
\newcommand{\cmax}{1-(P^*)^{\frac1{k-1}}}
\newcommand{\NewN}{M}
\newcommand{\thetavec}{\vec{\theta}}
\newcommand{\uvec}{\vec{u}}
\newcommand{\sigmavec}{\lambda}
\newcommand{\sigmacom}{\sigma}
\newcommand{\sigmascal}{\lambda}
\newcommand{\PstarB}{\mathcal{P}^*_B}
\newcommand{\Ymod}{Y'}
\newcommand{\ceil}{\mathrm{ceil}}
% How to state the common variance assumption at the beginning of lemmas, propositions and theorems
\newcommand{\homog}{Suppose $\lambda^2_x = \sigma^2>0\ \forall x$.  }
\newcommand{\algref}[1]{Alg.~\ref{#1}}

\usepackage{algorithm,algorithmic}
%****************************************************************************

@@

%% The next versions of the hyperref command are used if you adopt the
%% outdated latex-dvips-ps2pdf route in generating your pdf file. In
%% this case you can use ps or eps files for graphics, but not pdf, jpeg, png etc.
%% However, the final pdf file should embed all fonts required which means that you have to use file
%% formats which can embed fonts. Please note that the final PDF file will not be generated on your computer!
%% If you are using WinEdt or PCTeX, then use the following. If you are using
%% Y&Y TeX then replace "dvips" with "dvipsone"

@@

@@

% If you use theoremes
\newtheoremstyle{wsc}% hnamei
{3pt}% hSpace abovei
{3pt}% hSpace belowi
{}% hBody fonti
{}% hIndent amounti1
{\bf}% hTheorem head fontbf
{}% hPunctuation after theorem headi
{.5em}% hSpace after theorem headi2
{}% hTheorem head spec (can be left empty, meaning `normal')i

\theoremstyle{wsc}
\newtheorem{theorem}{Theorem}
\renewcommand{\thetheorem}{ \arabic{theorem}}
\newtheorem{corollary}[theorem]{Corollary}
\renewcommand{\thecorollary}{\arabic{corollary}}
\newtheorem{definition}{Definition}
\renewcommand{\thedefinition}{\arabic{definition}}

@@

%***************************************************************************
% AUTHOR: AUTHOR NAMES GO HERE
% FORMAT AUTHORS NAMES Like: Author1, Author2 and Author3 (last names)
%
%		You need to change the author listing below!
%               Please list ALL authors using last name only, separate by a comma except
%               for the last author, separate with "and"
%
\WSCpagesetup{Toscano, Frazier}

% AUTHOR: Enter the title, all letters in upper case
\title{ASYMPTOTIC VALIDITY OF A FULLY SEQUENTIAL ELIMINATION PROCEDURE FOR INDIFFERENCE-ZONE RANKING AND SELECTION WITH TIGHT BOUNDS ON PROBABILITY OF CORRECT SELECTION\LaTeX}

% AUTHOR: Enter the authors of the article, see end of the example document for further examples
\author{Saul Toscano\\ [12pt]
School of Operations Research and Information Engineering\\
Cornell University \\ 
206 Rhodes Hall \\
Ithaca, NY 14853, USA\\
% Multiple authors are entered as follows.
% You may also need to adjust the titlevbox size in the preamble - search for titlevboxsize
\and
Peter I. Frazier\\ [12pt]
School of Operations Research and Information Engineering \\
Cornell University \\ 
206 Rhodes Hall \\
Ithaca, NY 14853, USA
}

@@

\noindent Levent Yilmaz\\
Auburn University\\
Email: \href{mailto://wsc15yilmaz@gmail.com}{wsc15yilmaz@gmail.com}\\
\\
Wai Kin (Victor) Chan\\
Rensselaer Polytechnic Institute\\
Email: \href{mailto://wsc15chan@gmail.com}{wsc15chan@gmail.com}\\
\\
II-Chul Moon\\
KAIST\\
Email: \href{mailto://wsc15moon@gmail.com}{wsc15moon@gmail.com}\\
\\
Theresa M. K. Roeder\\
San Francisco State University\\
Email: \href{mailto://wsc15roeder@gmail.com}{wsc15roeder@gmail.com}\\

\section{OFTEN OBSERVED MISTAKES}

The following list comprises the most common sources of error that had to be corrected by previous editors. Please make sure to go through the following list and check that your paper is formatted correctly:

\begin{enumerate}
\item   The paper can be \textit{at most} 12 pages long (15 for tutorials and panel sessions). Longer papers cannot be published.
\item	Paper title and section titles are in ALL CAPS, subsections capitalize the first letter of important words. Please use the templates to use correct indents and spaces.
\item	Paper is letter format, not DinA 4 format. Please use the required margins (different on page 1 from the following pages).
\item	Use the correct running heads! Use the proceedings editors and chairs on page one, and use the last names separated by commas for the other pages. Don't forget that the last Last Name is preceded by ``, and ''
\item	Double check the citation format!
\item	Don't forget the ``author biographies'' section!
\item	Double-check that figures and tables are referenced in the text and have the correct caption format!
\item	Double check that the author section after the title is formatted correctly: the number of organizations defines the number of blocks, the number of blocks defines the layout.
\item	In the heading on the title page, country names should be in ALL CAPS.
\item	The first line of each paragraph is indented, with the exception of the first paragraph of a section or subsection.
\item	There should be extra lines before and after enumerations, lists, etc.
\end{enumerate}

% Please don't exchange the bibliographystyle style
\bibliographystyle{wsc}
% AUTHOR: Include your bib file here
\bibliography{demobib}

\section*{AUTHOR BIOGRAPHIES}

\noindent {\bf LEVENT YILMAZ} is Professor of Computer Science and Software Engineering at Auburn University with a joint appointment in Industrial and Systems Engineering. He holds M.S. and Ph.D. degrees in Computer Science from Virginia Tech. He is the founding organizer and General Chair of the Agent-Directed Simulation Conference series and is currently serving as the Editor-in-Chief of \textit{Simulation: Transactions of the SCS}. His email address is \email{wsc15yilmaz@gmail.com}. \\

\noindent {\bf WAI KIN (VICTOR) CHAN} is an Associate Professor of the Department of Industrial and Systems Engineering at the Rensselaer Polytechnic Institute, Troy, NY.  He holds a Ph.D. in industrial engineering and operations research from University of California, Berkeley. His research interests include discrete-event simulation, agent-based simulation, and their applications in social networks, service systems, transportation networks, energy markets, and manufacturing. He is a member of INFORMS, IIE, and IEEE. His e-mail address is \email{wsc15chan@gmail.com}.\\

\noindent {\bf II-CHUL MOON} is an assistant professor at the Department of Industrial and Systems Engineering, KAIST, Daejeon, Republic of Korea. His theoretic research focuses on the overlapping area of computer
science, management, sociology, and operations research. His practical research includes military command and control analysis, counterterrorism analysis, intelligence analysis, and disaster management; His email address is \email{wsc15moon@gmail.com}.\\

\noindent {\bf THERESA M. K. ROEDER} is an Associate Professor of Decision Sciences at San Francisco State University. She holds a PhD in Industrial Engineering and Operations Research from UC Berkeley. Her research interests lie in O.R. education and simulation modeling, especially in healthcare and higher education. Her email address is \email{wsc15roeder@gmail.com}.\\

\newpage

\begin{figure*}[htb]
{
\centering
First Name Last Name 1 \\
First Name Last Name 2 \\
\vspace{12pt}
Institution \\
Street Address 1 \\
Street Address 2 \\
City, ST Zip, COUNTRY
\caption{Example title page heading with 2 authors from the same institution.\label{fig: 2 same}}
}
\end{figure*}

\begin{figure*}[htb]
{
\centering
\begin{tabular}{ccc}
\phantom{Entries to adjust spacing - ignore} & \phantom{intermediate space} & \phantom{Entries to adjust spacing - ignore} \\
First Name Last Name 1 & & First Name Last Name 2 \\
\\
Institution 1 & & Institution 2 \\
Street Address 1 & & Street Address 1 \\
Street Address 2 & & Street Address 2 \\
City, ST Zip, COUNTRY & & City, ST Zip, COUNTRY
\end{tabular}
\caption{Example title page heading with 2 authors from different institutions.\label{fig: 2 different}}
}
\end{figure*}

\begin{figure*}[htb]
{
\centering
\begin{tabular}{ccc}
\phantom{This adjusts spacing - ignore} & \phantom{This adjusts spacing - ignore} & \phantom{This adjusts spacing - ignore} \\
First Name Last Name 1 & & First Name Last Name 2 \\
\\
Institution 1 & & Institution 2 \\
Street Address Line 1 & & Street Address Line 1 \\
Street Address Line 2 & & Street Address Line 2 \\
City, ST Zip, COUNTRY & & City, ST Zip, COUNTRY \\
\\
\\
& First Name Last Name 3 \\
\\
& Institution 3\\
& Street Address 1 \\
& Street Address 2 \\
& City, ST Zip, COUNTRY
\end{tabular}
\caption{Alternate example title page heading with 3 authors from different institutions. \label{fig: 3 different}}
}
\end{figure*}

\begin{figure*}[htb]
{
\centering
\begin{tabular}{ccc}
\phantom{Adjust spacing using these entries} & \phantom{intermediate space} & \phantom{Adjust spacing using these entries} \\
First Name Last Name 1 & & First Name Last Name 2 \\
\\
Institution 1 & & Institution 2 \\
Street Address Line 1 & & Street Address Line 1 \\
Street Address Line 2 & & Street Address Line 2 \\
City, ST Zip, COUNTRY & & City, ST Zip, COUNTRY \\
\\ \\
First Name Last Name 3 & & First Name Last Name 4 \\
\\
Institution 3 & & Institution 4 \\
Street Address Line 1 & & Street Address Line 1 \\
Street Address Line 2 & & Street Address Line 2 \\
City, ST Zip, COUNTRY & & City, ST Zip, COUNTRY
\end{tabular}
\caption{Example title page heading with 4 authors from different institutions.\label{fig: 4 different}}
}
\end{figure*}

>>>>

%**************************************************************************
%*
%*  Paper: ``INSTRUCTIONS FOR AUTHORS OF LATEX (Poster) ABSTRACTS''
%*
%*  Publication: 2011 Winter Simulation Conference Author Kit
%*
%*  Filename: wsc11poster.tex
%*
%*      DATE: Feb 08, 2011 to become the primary WSC'11 LaTeX file
%*
%*  Word Processing System: TeXnicCenter and MiKTeX
%*
%*
%*  All files need the following
\input{wsc15style.tex}     % download from author kit.  Style files for wsc formatting

\documentclass{wscposterproc}
\usepackage{latexsym}
%\usepackage{caption}
\usepackage{graphicx}
\usepackage{mathptmx}

%
%****************************************************************************
% AUTHOR: You may want to use some of these packages. (Optional)
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
%****************************************************************************

@@

%% The next versions of the hyperref command are used if you adopt the
%% traditional latex-dvips-ps2pdf route in generating your pdf file. In
%% this case you can use ps or eps files for graphics, but not pdf, jpeg, png etc.
%% If you are using WinEdt or PCTeX, then use the following. If you are using
%% Y&Y TeX then replace "dvips" with "dvipsone"

@@

%****************************************************************************
% AUTHOR: You may need to use the following command to adjust the space on the title page
% to properly list all authors.
% Please use: 2.5in for 1 row of authors, 3.75in [default] for 2 rows of authors
%\setlength{\titlevboxsize}{2.5in}  % 2.5in for 1 row of authors, 3.75in for 2 rows of authors
%****************************************************************************

@@

@@

%***************************************************************************
% AUTHOR: AUTHOR NAMES GO HERE
% FORMAT AUTHORS NAMES Like: Author1, Author2 and Author3 (last names)
%
%		You need to change the author listing below!
%               Please list ALL authors using last name only, separate by a comma except
%               for the last author, separate with "and"
%
% These names will be used from the 2nd page on - thus for one page abstracts this can stay as it is.
% DON'T REMOVE THIS LINE!
%
\WSCpagesetup{LastName1, LastName2, and LastNameLastAuthor}

% AUTHOR: Enter the title, all letters in upper case
\title{INSTRUCTIONS FOR AUTHORS OF POSTER ABSTRACTS USING \LaTeX}

% AUTHOR: Enter the author(s) of the poster abstract
\author{Levent Yilmaz \\[12pt]
Computer Science and Software Engineering\\
Auburn University \\
3116 Shelby Center\\
Auburn, AL 36849, USA
}

@@

\noindent Levent Yilmaz\\
Auburn University\\
Email: \href{mailto://wsc15yilmaz@gmail.com}{wsc15yilmaz@gmail.com}\\
\\
Wai Kin (Victor) Chan\\
Rensselaer Polytechnic Institute\\
Email: \href{mailto://wsc15chan@gmail.com}{wsc15chan@gmail.com}\\
\\
II-Chul Moon\\
KAIST\\
Email: \href{mailto://wsc15moon@gmail.com}{wsc15moon@gmail.com}\\
\\
Theresa M. K. Roeder\\
San Francisco State University\\
Email: \href{mailto://wsc15roeder@gmail.com}{wsc15roeder@gmail.com}\\
\\
% Please don't exchange the bibliographystyle style
\bibliographystyle{wsc}
% AUTHOR: Include your bib file here
\bibliography{demobib}
